---
title: "Untitled"
author: "Maggi Brisbin"
date: "1/15/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(stringr)
library(dplyr)
library(ggplot2)

library(ggtree)
library(treeio)
library(tidytree)
`%ni%` = Negate(`%in%`)

colors=c('#e9e9e9','#C14450','#f3757b','#f0b08f','#c2aba6','#60555f','#232229','#3c6481','#9fd6e6','#256F64','#63a375')

tre <-read.newick("~/Desktop/PhaeoPhycosphere/recruitmentStudy/MC_rooted-fasttree-tree.nwk/tree.nwk", node.label = "label")

ggtree(tre)
```

```{r}
bubble_data<-read.csv("bubbleplot_df.csv")
names(bubble_data)[1] <- "label"
bubble_data$Order<-str_sub(bubble_data$Order, 5, str_length(bubble_data$Order))
bubble_data$Phylum<-str_sub(bubble_data$Phylum, 5, str_length(bubble_data$Phylum))
bubble_data$Class<-str_sub(bubble_data$Class, 5, str_length(bubble_data$Class))
```

step 1. prune tree to only include ASVs in this set: 

```{r}

x<-as_tibble(tre)

dfx<- as.data.frame(x)
#make list "to drop"
todrop <- dfx[dfx$label %ni% unique(bubble_data$label),]$label

reduced <- drop.tip(tre, todrop)
```

```{r}
ggtree(reduced) +geom_tiplab(size=0, align=TRUE, linesize=.05)
```
Step 2. annotate and format tree as desired (colors for groups, etc.)

```{r}
#add order to tibble to line up node numbers with Order 

TaxaData <- bubble_data %>%  dplyr::select(label, Phylum, Class, Order)
TaxaData <-TaxaData[!duplicated(TaxaData$label),]

x<- as_tibble(reduced)

y <- full_join(x, TaxaData, by = 'label')

reduced4plot <- as.treedata(y)

Oceanospirillales_node<- ancestor(y, "787644618b763435c4533db8160a05c3")

treeplot<- ggtree(reduced4plot, aes(color=Phylum)) + geom_cladelabel(node=1151, label="Oceanospirillales", angle =270,  align=FALSE, offset.text=.008, hjust='center', fontsize = 2) +theme_tree() + theme(legend.position = "none")

treeplot
```


Step 3. Make heatplot with relative abundandances 

```{r}
#facet_plot(treeplot, panel = "RelAbund", data = bubble_data[bubble_data$Abundance >0,], geom = geom_point, mapping=aes(x = SampleName, color = "black", size = Abundance)) 
```


```{r}
abundanceSub <- read.csv("abundanceSubset.csv")
abundanceSub$label <- as.character(abundanceSub$label)
row.names(abundanceSub) <- abundanceSub$label
abundanceSub<- abundanceSub[,-1]

```



```{r}
library(ggnewscale)

p1 <- gheatmap(treeplot, abundanceSub, colnames=FALSE) + 
     scale_fill_gradient(low="white", high="red",    
                   breaks=seq(0,1,0.25), 
                   limits=c(0, 50))  + theme(legend.position = "none")

p2 <- p1 + new_scale_fill()
gheatmap(p2, abundanceSub, offset=1,
         colnames_angle=90, colnames_offset_y = .25)  + 
     scale_fill_gradient(low="white", high="red",    
                   breaks=seq(0,100,25), 
                   limits=c(0, 50)) + theme(legend.position = "none")


p3 <- p2 + new_scale_fill()
gheatmap(p3, abundanceSub, offset=1,
         colnames_angle=90, colnames_offset_y = .25)  + theme(legend.position="none")


```







Step 4. put together tree and heat plot

### maybe this would be more useful if only included the taxa in recruited/original and not the ones that were in SW but not in the cultures? 
 the empty space is compelling but....
 
```{r}
bubble_data<-read.csv("microbiomemeta.csv")
names(bubble_data)[1] <- "label"
bubble_data$Order<-str_sub(bubble_data$Order, 5, str_length(bubble_data$Order))
bubble_data$Phylum<-str_sub(bubble_data$Phylum, 5, str_length(bubble_data$Phylum))
bubble_data$Class<-str_sub(bubble_data$Class, 5, str_length(bubble_data$Class))
```

step 1. prune tree to only include ASVs in this set: 

```{r}

x<-as_tibble(tre)

dfx<- as.data.frame(x)
#make list "to drop"
todrop <- dfx[dfx$label %ni% unique(bubble_data$label),]$label

reduced <- drop.tip(tre, todrop)

x<- as_tibble(reduced)

TaxaData <- bubble_data %>%  dplyr::select(label, Phylum, Class, Order)
TaxaData <-TaxaData[!duplicated(TaxaData$label),]

y <- full_join(x, TaxaData, by = 'label')

reduced4plot <- as.treedata(y)


Oceanospirillales_node<- ancestor(y, "787644618b763435c4533db8160a05c3")
altero <- ancestor(y, "2178df8b26afebada98155b8cad0c967")
entero <- ancestor(y, "20a8421dc461b541f429438b3b76ec35")
vibrio <- ancestor(y, "1ae434de7911786ccf390031af76391c")

```

```{r}
ggtree(reduced4plot) +geom_tiplab(size=0, align=TRUE, linesize=.05)  

  
```
 
```{r}
library(ape)

pdf("tree.pdf")
plot(reduced, show.tip.label = FALSE)
nodelabels()
dev.o
```
 
